\documentclass[preprint,12pt]{elsarticle}

% additional packages
\usepackage[utf8]{inputenc}
%\bibliographystyle{abbrvnat}
\usepackage{gensymb}
\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{subcaption}
\usepackage{tabularx}
\usepackage{array,multirow,multicol,graphicx}
\usepackage{comment}
\graphicspath{
  {./../figures/},
}
\usepackage{lineno}
\linenumbers
% macros

\journal{Building and Environment}

\begin{document}

\begin{frontmatter}
% title
\title{Sorption Phenomena In Transient Vapor Intrusion Scenarios}

% authors
\author[Brown]{Jonathan G. V. Ström}
\author[Brown]{Shuai Xie}
\author[Brown]{Eric M. Suuberg}


\ead{eric\_suuberg@brown.edu}
\address{These authors contributed equally to this work}
\address[Brown]{Brown University, School of Engineering, Providence, RI, USA}

\begin{abstract}
\input{abstract.tex}
\end{abstract}

\begin{keyword}
  Vapor intrusion \sep Temporal variability \sep Sorption \sep Attenuation factor
\end{keyword}

\end{frontmatter}

\input{intro.tex}
\input{methods.tex}
\input{results.tex}
\input{conclusions.tex}

\section*{Acknowledgements}
This project was supported by grant ES-201502 from the Strategic Environmental Research and Development Program and Environmental Security Technology Certification Program (SERDP-ESTCP).\par

Declaration of interest: none

\clearpage
\input{appendix.tex}

\bibliographystyle{elsarticle-num}
\bibliography{references}


\begin{comment}
Main point of this paper:

To explore how sorption affects VI transport in soils and indoor environment,
and the effect that sorption has on efficacy of mitigation systems

Outline:

Introduction:
* Why study sorption in VI?
- Many materials (significantly) sorb VI contaminants.
- No previous studies.
- May significantly affect:
-- Mitigation
-- VI investigations

* What are we gonna do to bridge till gap?
- Measure sorptive capacities at relevant concentrations. Why?
-- Isotherms non-linear w.r.t. concentration & few studies at VI relevant conditions.
-- Pick TCE (contaminant of significant concern).
- Apply results in our VI model.
-- Used extensively before
-- In lieu of a study house this will give some insights

* Outline
- Experimental setup
- Numerical model & governing equations
- Results regarding:
-- Soil transport & sorption
-- Indoor environment transport & sorption (specifically how response of c_in w.r.t. pressurization changes).
-- Reduction of mitigation system efficacy




\end{comment}

\end{document}
